Title?

### 2018-04-27 paper_wc.tex
Last corollary!

@@

local auctions on each other. We have the following Lemma,

@@

profiles, where buyer bid $s_i^j > 0 \Rightarrow j\in\mcI_i$. It follows from
(\ref{lambda}) and (\ref{llambda}) that $\Delta$ is defined by a seller $j\in\mcI$, where each
user $k\in\Delta$ has some direct or indirect influence on $j$. 
We may identify $\Delta$ by its dominant seller, and we let $\Delta^j$ denote $j$'s
influencing sets. We have that, 

@@

shift, caused by the underlying dynamics.
Consider $k\in\mcI^j$ where, for example, some buyer(s) enter the auction and

@@

$s_k^j>0$ at time $t$ will cause a transition, where, by Proposition \ref{buyerstrategy}, $k$ will set its bid $s_i^j=0$, and begin to add sellers to its pool.
Suppose that at time $t$, $j$'s market is at equilibrium, i.e. $\sum_{i\in\mcI^j} = D^j$, and
no buyer rebids. Unless $k$ adds a seller with a higher reserve

@@

auction will end. Otherwise, at some time $t\in[t+1,\tau]$, we must have that $\g_k^j <
D^j$, and $k$ opts-out. Finally, overlooking market transitions and messaging

@@

Now, the subset $\mcI^j \subset \mcI$
determines $j$'s reserve price $p_{i^*}^j$. We will assume the buyer submits a
coordinated, truthful bid. Now, $\mcI_i\subset \mcI$ 
determines the unit price $p_{i}$ in buyer $i$'s bid.
The reserve price (\ref{newprice}) of seller $j$ is determined at each
transition, and is
the lowest price that $j$ will accept to perform any allocation.
Let $p_*^j = f^j \circ \g_i^j(a) $ denote the reserve
price of auction $j$, noting that $s_i^j=0, \ \forall \ i \in
[s_i^j]_{i\ni\mcI^j}$, and let $p_i^*= f_i \circ \g_i^j(a)$ denote the bid price of buyer $i$, i.e. $p_i^k = p_i^*,
\ \forall \ k \in\mcI_i$. 
Using Proposition
\ref{sellerstrategy}, for each $i \in \mcI^j$, we have from (\ref{buyerinversedemand}), (\ref{sellerinversedemand}), that $p_i^* \ge p_*^k,
\ \forall \ k \in\mcI_i$.

@@

The incentive of each seller $\in\Lambda$ is to sell all of its data at the
best possible price. In the simplest case,
consider a disjoint local market $j$, where $\forall \ i\in\mcI^j$, $s_i^k = 0,
\ \forall \ k\ne j \in \mcI_i \Rightarrow \Lambda = \lbrace j \rbrace$ and
$\lambda = \mcI^j$. 
Again using (\ref{buyerinversedemand}) and  (\ref{sellerinversedemand}), it is
clear that $\theta_i = \theta^j, \ \forall \ i \in \mcI^j$.
In all other cases, the sellers $\in\Lambda$ are competing to sell
their respective resources to buyers whose valuations are distributed across multiple auctions. 
%By (\ref{jtoi}), $j\in \mcI_i, \ \forall \ i\in \mcI^j$. 
The set $\lambda$ represents all of the buyers influencing auction $j$, both
directly and indirectly. 
The bid price of buyer $i\in\mcI^j$ is determined by,
\begin{equation}\label{maxbid}
    p_i^* = \max_{k\in\mcI_i}\big(f^k \circ \g_i(a)\big)= \max_{k\in\mcI_i}(p_*^k).
\end{equation}
$\Lambda$ is the set of sellers directly influencing the bids of buyers
in auction $j$. Now, the reserve price for auction $j$ is such that,
\begin{equation}\label{resprice}
    p_*^j \le \min_{i\in\mcI^j}(p_i^*) - \epsilon,
\end{equation}
by Proposition \ref{sellerstrategy}. 
Also, in the absence of transitions, caused by multi-auction market dynamics, we have 
that $j$ maintains a local market
equilibrium from time $t$ to $(t+1)$.
Consider a subset $\Delta^j$, by
Proposition \ref{userunion}, a transition occurs in 2 cases. (1) If $i\in\mcI^j$
decreases its bid quantity so that $\sum_{i\in\mcI^j}
\g_i^j(a) < D^j$, and (2) buyer $i^*$, defined in Proposition
\ref{sellerstrategy} increases its valuation so that $p_{i^*}^j <
p_*^j$. Clearly, if $i^*$ increases its valuation,
then $p_*^j$ will similarly increase, by (\ref{uservaluation}). Now, consider a
seller $k^*\in\mcI_{i^*}$. Since $p_{i^*}^j <
p_*^j$, we have that $k^*\ni\Lambda\subset \Delta^j\Rightarrow \mcI^{k^*} \ni
\lambda$. Now, suppose at the end of some time step, $p_*^{k^*} > p_*^j$, and
consider a buyer $l^*\in\mcI^{k^*}$. Clearly, if $l^*\in\mcI^j$, then $j$'s
valuation wil increase. Suppose $l^*\ni\mcI^j$, from Proposition \ref{userunion}, if $l^*\in\mcI^k\subset
\Delta^j$, for some $k\in\mcI_i$, where $i\in\Delta^j$, then either
$k^*\ni\mcI_i$ or $\exists \ q\in\mcI_i$ such that $p_*^q \ge p_*^{k^*}$. In
the former case, the valuation of $k\in\mcI_i$ and $j$ will increase.
In the latter case, $p_*^q \ge p_*^{k^*}$ for some
$q\in\mcI_i$, and then only the valuation of $j$ will increase. We have that $j$ is
directly influenced by our choice of seller $k^*$, and observe that
$i\in\mcI^j$ is free to increase its valuation within $\Delta^j$.

Let buyer $i\in\mcI^j$ be the buyer in auction $j$ with the lowest bid price,
and further suppose $p_i^* > p_*^j + \epsilon$. That is, $\exists \ q \in \mcI_i$ such
that $p_*^q > p_*^j$. Fixing all other bids, a decrease in $q$'s demand from time $t$ to $t+1$ will
directly impact buyer $i$. If at time $t+1$ we still have that $i$ is the
buyer with the lowest bid price, then (\ref{sellerinversedemand}) holds and
thus $j$'s valuation does not change. Otherwise a new buyer with the lowest bid will be chosen upon
recomputing $\mcI^j$, as in Proposition \ref{buyerstrategy}. 
In each case we
have that (\ref{buyerinversedemand}) and (\ref{sellerinversedemand}) hold for
some fixed time $t$, and so, $\forall \ i \in\mcI^j$,
\begin{equation}\label{jdemand}
    \int_0^{\g_i^j(a)} f^j(z) \ dz 
    = \int_0^{\g_i^j(a)} f_i(z) \ dz,
\end{equation}
therefore $\theta_i = \theta^j, \ \forall \ i \in \mcI^j$.

Consider the set $\lambda$. For some buyer $i\in\mcI^j$, and then for
some seller $k \in \mcI_i$, we have a buyer $l \in \mcI^k$. By (\ref{jtoi}), $i,l \in \mcI^k$, and so the reserve price $p_*^k \le \min(p_l^*,
p_i^*)$, and $k, j\in \mcI_i\Rightarrow p_i^* \ge \max(p_*^k, p_*^j)$.
Suppose that $l \ni \mcI^j\Leftrightarrow j \ni \mcI_l$, so
that $p_l^* < p_*^j$, and
the valuation of buyer $l$ does not impact auction $j$ and vice versa, i.e. $\theta_l^j = 0$. Since $l\in\mcI^k$, $p_l^* \ge p_*^k\Rightarrow
p_*^k < p_*^j$, and $i\in\mcI^j \Rightarrow p_i^* \ge p_*^j$, so,
$$
    p_*^k \le p_l^* < p_*^j \le p_i^*,
$$
for any buyer $l\in\lambda$ such that $l\ni \mcI^j$. Now, suppose $\exists \ l\in\mcI^k$ such that $l\in\mcI^j \Rightarrow p_l^* \ge
p_*^j$. In the case where $p_l^* > p_i^*$, we must have that 
$\exists \ q \in \mcI_l$ such that $p_*^q > p_*^k$, % \Rightarrow \theta_l^q > \theta_l^k$. 
which implies, again by (\ref{maxbid}), $q\ni\mcI_i \Leftrightarrow i
\ni\mcI^q \Rightarrow p_*^q >
p_i^*$, therefore $\theta_i^q = 0$, and the reserve price of auction $q$ does not effect the valuation of
buyer $i$. 
Lastly, in the case where $p_i^* > p_l^*$, by the same reasoning, $\theta_l^q =
0$ for $q\in\mcI_i$.
We have that for any $l\in\mcI^k$ such that $l\ni
\mcI^j$, $\theta_l^j =0$, and when $l\in \mcI^j$, then either $\theta_i^q =0$
for $q\in\mcI_l$ or $\theta_l^q = 0$ for some $q\in\mcI_i$. Thus, any bid ouside of
our construction
has a zero valuation, with respect to buyers $\in\lambda$ and sellers
$\in\Lambda$, and therefore cannot cause transitions to occur except through a
shared buyer, e.g. some $l\in\mcI^k$. Thus, in all cases,
(\ref{buyerinversedemand}) and (\ref{sellerinversedemand}) hold. Fixing all
bids in any auction $\mcI^q$, where $q\in \mcI_l \setminus \Lambda$,
we have, $\forall \ k\in\mcI_i$,
\begin{equation}\label{idemand}
    \displaystyle\int_0^{D^k} f^k(z) \ dz = \sum_{i\in\mcI^k}\int_0^{\g_i^k(a)}
f^k(z) \ dz,
\end{equation}
which holds $\forall \ k\in\mcI_i$, by (\ref{jtoi}) and Proposition
\ref{sellerstrategy}..
Finally, using (\ref{jdemand}), (\ref{idemand}), $\forall \ i\in\mcI^j, \forall \ k\in\mcI_i,\forall \ l\in\mcI^k$,
\begin{align}\label{tieqtk}
    \int_0^{\g_i^k(a)} f_i(z) \ dz &= \int_0^{\g_i^k(a)} f^k(z) \ dz,
\end{align}
and
\begin{align}\label{tkeqtl}
    \int_0^{\g_l^k(a)} f^k(z) \ dz &= \int_0^{\g_l^k(a)} f_l(z) \ dz.
\end{align}
Thus, with a slight abuse of notation for clarity,
\begin{equation}\label{funion-eq}
    \sum_{\lambda}\int_0^{\g(a)} f^\Lambda(z) \ dz =
\sum_{\Lambda}\int_0^{\g(a)} f_\lambda(z) \ dz,
\end{equation}
where the result follows by construction, and the continuity of $\theta'$.
$\qed$

@@

In order to represent the public platform of the secondary market, we model the ISP as
a kind of buyer $\kappa$ who remains at time $t=0$, i.e. does not participate
in any auctions. At time $t=0$, a seller $k$ entering the market will have
submitted bid $s_\kappa^j =(\epsilon, D^j)$ to the CMHK platform, and so the
seller does not require a priori demand information to enter the market.
(DO I WANT UPDATES? MORE OR LESS FAIR? NEED EITHER UPDATE QUANTITY OR BOTH,
IMPLICATIONS?)
We assume that sellers update their bids with the ISP, which is modeled as a
``buyer" $\kappa$. 
A new sellers' bid, $(D^j, \epsilon)$, as well as updated bids(NOT SURE), is public
knowledge. 
\iffalse
A buyer entering the market
at $t=0$ is assumed to have an initial nonzero bid price, which we may assume
(SAY BETTER!) is initialized as 
an independently and identically distributed (i.i.d.) random variable $p_i^j=X$ with
probability $\mathcal{P}$,
$$
    \mathcal{P}[\epsilon\le X \le \kappa] =
\displaystyle\int_\epsilon^{p^\kappa} \mathfrak{f}(x) \
ds,
$$
where $p^\kappa$ is the overage charge of the ISP, and $\mathfrak{f}$ the probability
density function of $X$.
\fi
%may represent by some homogenous function of degree one (EXPAND?). 
Thus the auction
begins at time $t>0$, and at $t=0$, $j$ will increment through a single iteration,
initializing bid prices.

Consider a user seeking to prevent
data overage charges by purchasing data from a subset of other network users.
The sellers' auction will function as follows: at each bid iteration all buyers
submit bids, and the winning bid is the buyer $i$ that has the highest price
$p_i^j$. The seller allocates
data to this winner, at which point all other buyers are able to bid again, and
the winner leaves the auction (with the exception where multiple bidders bid
the same price, where (\ref{dataallocation}) determines they will not fully
satisfy their demand, and so we will assume they remain in the auction). The auction progresses as such until all the
sellers' data has been allocated. 
% SELLER ALGORITHM
\begin{center}
\begin{algorithm}[H]
\caption{(Seller progressive allocation)}
\begin{algorithmic}[1]
\State $p^{j(0)} \gets \epsilon$, $s^{j(0)} \gets (p^j, D^j)$, $\bar\mcI =
\emptyset$, compute
$\mcI^{j(0)}$
\State Update $s^j$ 
\While{$D^j(t) > 0$}
\State $\bar{i} \gets \displaystyle\max_{i\in I^j}\sum_{i\in I^j} p_i^j$ 
\State $D^{j(t+1)} \gets D^{j(t)} - \g_{\bar{i}}^{j(t)}(a)$
%\State $p^j \gets \theta_{i^*}'(d_{i^*}^j)\circ e_i$
\State $p^j \gets p_{i^*}^j+\epsilon$ and $d^j \gets D^{j(t+1)}$
\State $s^{j(t+1)} \gets (d^j, p^j)$
\State Update $s^j$
\State $\bar\mcI \gets \bar\mcI \cup \bar{i}$
\For{$k \in \bar\mcI$}
\If{$p_k^j < p_{i*}^j$}
\State $D^{j(t+1)} = d_k^{j}$
\State $\bar\mcI \gets \bar\mcI \setminus \lbrace k \rbrace$
\EndIf
\EndFor
\State Compute $\mcI^{j(t)}$
\State $\mcI^{j(t+1)} = \mcI^{j(t)}\setminus \bar\mcI$
\State $t \gets t+1$
\EndWhile
\end{algorithmic}
\end{algorithm}
\end{center}
Each time step, $s^j$ is updated it is shared with all
participating buyers. At this point buyers have the opportunity to bid again,
where a buyer that does not bid again is assumed to hold the same bid, since a
buyer dropping out of the auction will set their bid to $s_i^j=(0,0)$. We
define a single iteration of the auction, wher a seller updates bid vector
$s^j$, and the buyers' response $s_i$, to comprise a single time step.

@@

The property of truthfullness is an essential component of equilibrium in
second-price markets. The strategies described in this paper have removed the
necessity for a user to determine its own valuation function, we intend to show that the market dynamics resulting from the
construction of the user strategy space results in truthful bids that are optimal for all users,
i.e. bid prices are to the marginal value as determined by market dynamics. 
To achieve incentive compatibility, we find that the opt-out buyer must choose
this subset so that its overall marginal value is greater than its market price.
We have so far only made the \emph{assumption} of truthful bids throughout our analysis. As was shown in Lemma \ref{userunion}, a buyer only
has incentive to change its bid as a result of a market shift or partial
allocation. We now show the necessary condition of a truthful reply, new bid
prices must differ from the last by at least $\epsilon$, and prove that the
resulting bid is an $\epsilon$-best response, supporting our strategic analysis.
In a truthful reply, the term $\epsilon/\theta_i'(0)$
ensures that a new bid price differs from the last bid price by at least
$\epsilon$, thereby ensuring that a buyer does not change its bid without
correcting the effects of unstable transitions.
We argue that if truthfulness holds \emph{locally} for both buyers and sellers, i.e. $p_i ={\theta_i}' \
\forall \ j \in \mcI_i$ and $p^j = {\theta^j}' \ \forall \ i \in\mcI^j$, then
there exists a local market equilibrium extending over a subset of connected
local markets. We have the following Proposition. 
(DO I NEED TO PROVE CONTINUITY TOO?)

@@

\proposition{(Incentive compatibility across local auctions)}

@@

\corollary{Seller cooperation.}

@@

The data-sharing market consists of a inter-dependent sets of these
multi-auction games around fixed points.  Clearly, the union of all possible
sets $\bigcup_{j\in\mcI} \Delta^j$ covers $\mcI$. Consider two subsets, $\Delta^j$
and $\Delta^k$, at equilibrium, and a shared
buyer $i\in (\lambda^j \cup \lambda^k)$, where
$\lambda^j\subset\Delta^j$, and  $\lambda^k\subset \Delta^k$.  By Lemma
\ref{userunion}, a transition is induced in $\Delta^k$ by $\Delta^j$ if and only if
$\exists \ l \in \Lambda^j$ such that $p_*^{l} > p_*^{q}$, for some
$q\in\Lambda^k$. We claim that the shared buyers
between the different subsets $\Delta$ form a heirarchical structure, and that
there can only be a single primary fixed point, and this seller determines
the equilibrium price in the global market. Now, consider the set of sellers across all $\Delta$,
$\bigcup_{j\in\mcI}\Lambda^j$.

%Consider
%again $q\in\mcI_i$, and the subset $\Delta^q$, where $p_*^q \ge p_*^j$, and
%a buyer $l\in\lambda\subset\Delta^q$ chosen in the same way as $l^*$.

A Nash equilibrium is defined as a strategy vector, or, in terms of PSP, a bid
profile $s$,
from which no player has a unilateral incentive to deviate (Johari, 2004)
(EXPAND)
We first show the existence of a \emph{static} Nash equilibrium, where buyers have fixed reserve
prices.

{
\lemma{(Static Nash Equilibrium)} 
}

>>>>

\subsection{Motivation for Privacy/Security}(NEW SECTION)

A property of PSP is that the user valuations are held private.

1. The seller doesn't update with the ISP, and so does not know the market price
 in the data-exchange market.\\
2. The auction is distributed, so there is no collusion between sellers and
ISP.\\
3. The mechanism is self-contained, and only requires participation. (THINK!)
4. Better economy, as few users will get data plans with a lot of data, make
money, allowing others to have cheaper data plans and not pay a lot for
texting, phone calls (Buzzfeed). Free market capitalism! \\
(CONCERN HERE ABOUT THROTTLING)

@@

local auctions on each other. Defining a single iteration of the auction, where a seller updates bid vector
$s^j$, and the buyers' response $s_i$, to comprise a single time step, and we have the following Lemma,

@@

profiles, where buyer bid $s_i^j > 0 \Rightarrow j\in\mcI_i$. Using Proposition \ref{sellerstrategy} and (\ref{jtoi}), we have that, 

@@

shift caused by the underlying dynamics.
Consider $k\in\mcI^j$ at time $t$ where, for example, some buyer(s) enter the auction, and

@@

$s_k^j>0$ will cause $k$ to initiate a shift. By Proposition \ref{buyerstrategy}, $k$ will set $s_k^j=0$, and begin to add sellers to its pool.
Suppose that at time $t$, $j$'s market is at equilibrium, i.e.
$\sum_{i\in\mcI^j} \g_i^j(a) = D^j$, and fixing all other bids, so 
no buyer $i\in\mcI^j$ rebids. Unless $k$ adds a seller with a higher reserve

@@

auction ends. Otherwise, at some time $t\in[t+1,\tau]$, we must have that
$\g_k^j \le D^j$, and $k$ rejoins auction $j$ or opts-out. Finally, overlooking market shifts and messaging

@@

Now, the subset $\mcI^j \subset \mcI$
determines $j$'s reserve price $p_{i^*}^j$. We will assume the buyer submits a
coordinated, truthful bid. Now, $\mcI_i\subset \mcI$ 
determines the unit price $p_{i}$ in buyer $i$'s bid.
The reserve price (\ref{newprice}) of seller $j$ is determined at each
shift, and is
the lowest price that $j$ will accept to perform any allocation.
Let $p_*^j = f^j \circ \g_i^j(a) $ denote the reserve
price of auction $j$, noting that $s_i^j=0, \ \forall \ i \in
[s_i^j]_{i\ni\mcI^j}$, and let $p_i^*= f_i \circ \g_i^j(a)$ denote the bid price of buyer $i$, i.e. $p_i^k = p_i^*,
\ \forall \ k \in\mcI_i$. 
Using Proposition
\ref{sellerstrategy}, for each $i \in \mcI^j$, we have from (\ref{buyerinversedemand}), (\ref{sellerinversedemand}), that $p_i^* \ge p_*^k,
\ \forall \ k \in\mcI_i$.

@@

The incentive of each seller $\in\Lambda$ is to sell all of its data at the
best possible price. In the simplest case,
consider a disjoint local market $j$, where $\forall \ i\in\mcI^j$, $s_i^k = 0,
\ \forall \ k\ne j \in \mcI_i \Rightarrow \Lambda = \lbrace j \rbrace$ and
$\lambda = \mcI^j$. 
Again using (\ref{buyerinversedemand}) and  (\ref{sellerinversedemand}), it is
clear that $\theta_i = \theta^j, \ \forall \ i \in \mcI^j$.
In all other cases, the sellers $\in\Lambda$ are competing to sell
their respective resources to buyers whose valuations are distributed across multiple auctions. 
%By (\ref{jtoi}), $j\in \mcI_i, \ \forall \ i\in \mcI^j$. 
The set $\lambda$ represents all of the buyers influencing auction $j$, both
directly and indirectly. 
The bid price of buyer $i\in\mcI^j$ is determined by,
\begin{equation}\label{maxbid}
    p_i^* = \max_{k\in\mcI_i}\big(f^k \circ \g_i(a)\big)= \max_{k\in\mcI_i}(p_*^k).
\end{equation}
$\Lambda$ is the set of sellers directly influencing the bids of buyers
in auction $j$. Now, the reserve price for auction $j$ is such that,
\begin{equation}\label{resprice}
    p_*^j \le \min_{i\in\mcI^j}(p_i^*) - \epsilon,
\end{equation}
from (\ref{newprice}). Now, by Proposition \ref{sellerstrategy}, in the absence
of external influences caused by multi-auction market dynamics, we have 
that $j$ maintains a local market equilibrium from time $t$ to $(t+1)$.
From (\ref{lambda}) and (\ref{llambda}), $\Delta$ is defined by a seller $j\in\mcI$, where each
user $k\in\Delta$ has some direct or indirect influence on $j$. 
We may identify $\Delta$ by its dominant seller, and we denote $\Delta^j = \Lambda^j
\cup \lambda^j$.

Consider the set $\lambda^j$. For some buyer $i\in\mcI^j$, and then for
some seller $k \in \mcI_i$, we have a buyer $l \in \mcI^k$. By (\ref{jtoi}), $i,l \in \mcI^k$, and so the reserve price $p_*^k \le \min(p_l^*,
p_i^*)$, and $k, j\in \mcI_i\Rightarrow p_i^* \ge \max(p_*^k, p_*^j)$.
Suppose that $l \ni \mcI^j\Leftrightarrow j \ni \mcI_l$, so
that $p_l^* < p_*^j$, and
the valuation of buyer $l$ does not impact auction $j$ and vice versa, i.e. $\theta_l^j = 0$. Since $l\in\mcI^k$, $p_l^* \ge p_*^k\Rightarrow
p_*^k < p_*^j$, and $i\in\mcI^j \Rightarrow p_i^* \ge p_*^j$, so, $p_*^k \le
p_l^* < p_*^j \le p_i^*$, %<---- MAKE AN EQUATION?
for any buyer $l\in\lambda^j$ such that $l\ni \mcI^j$. Now, suppose $\exists \ l\in\mcI^k$ such that $l\in\mcI^j \Rightarrow p_l^* \ge
p_*^j$. In the case where $p_l^* > p_i^*$, we must have that 
$\exists \ q \in \mcI_l$ such that $p_*^q > p_*^k$, % \Rightarrow \theta_l^q > \theta_l^k$. 
which implies, again by (\ref{maxbid}), $q\ni\mcI_i \Leftrightarrow i
\ni\mcI^q \Rightarrow p_*^q >
p_i^*$, therefore $\theta_i^q = 0$, and the reserve price of auction $q$ does not effect the valuation of
buyer $i$, and as $p_*^k < p_*^j \le p_i^* < p_l^*$, we examine $\mcI^j$ using
(\ref{iff}).
Lastly, in the case where $p_i^* > p_l^*$, by the same reasoning, $\theta_l^g =
0$, for some $g\in\mcI_i$.
We have that for any $l\in\mcI^k$ such that $l\ni
\mcI^j$, $\theta_l^j =0$, and when $l\in \mcI^j$, then either $\theta_i^q =0$,
where $q\in\mcI_l$, or $\theta_l^g = 0$, where $g\in\mcI_i$, and as $p_*^k <
p_*^j \le p_l^* < p_i^*$, we examine $\mcI^k$ using (\ref{iff}),
a shift in $\mcI^k$ causes a shift in $\mcI_i$, so that $\exists \ g\in\mcI_i$
such that $p_*^g \ge p_*^j$. Thus, we
determine a direct influence as $l\in\mcI^k
\cap \Lambda^j$, such that $p_l^* > p_i^*$,
and an indirect influence as, for any $l\in\mcI^k
\setminus \Lambda^j$, where $p_l^* > p_i^*$ results in $i^*\in\mcI^j$ initiating a shift.

Now, consider the subset $\Lambda^j$, by
Proposition \ref{userunion}, a shift occurs in 2 cases. (1) If $i\in\mcI^j$
decreases its bid quantity so that $\sum_{i\in\mcI^j}
\g_i^j(a) < D^j$, and (2) if buyer $i^*$, defined in Proposition
\ref{sellerstrategy}, increases its valuation so that $p_{i^*}^j <
p_*^j$. First, let buyer $i\in\mcI^j$ be the buyer in auction $j$ with the lowest bid price,
and further suppose $p_i^* > p_*^j + \epsilon$. That is, $\exists \ q \in \mcI_i$ such
that $p_*^q > p_*^j$. Fixing all other bids, a decrease in $q$'s demand will
directly impact buyer $i$. If at the end of the bid iteration, we still have that $i$ is the
buyer with the lowest bid price, then (\ref{sellerinversedemand}) holds and $j$'s valuation does not change. Otherwise a new $i^*$ will be chosen upon
recomputing $\mcI^j$, as in Proposition \ref{buyerstrategy}, and the market
will attempt to regain equilibrium.
Clearly, if $i^*$ in case (1) or resulting from case (2) increases in valuation,
then $p_*^j$ will similarly increase, by (\ref{uservaluation}). Consider the 
seller $k^*\in\mcI_{i^*}$ at time $t$, and suppose that $p_*^{k^*} \ge p_*^j$, however, we have that $p_{i^*}^j <
p_*^j \Rightarrow i^* \ni \mcI^j \Rightarrow k^*\ni\Lambda^j\Rightarrow \mcI^{k^*} \ni
\lambda^j$. Now, consider a buyer $l^*\in\mcI^{k^*}$. We need only consider the
case where $\exists \ k \in\Lambda^j$ such that $l^*\in\mcI^k\subset \lambda^j$
where we determine the influence of $\Delta^{k^*}$ on $\Delta^j$ by (\ref{iff}).

In each case we
have that (\ref{buyerinversedemand}) and (\ref{sellerinversedemand}) hold for
some fixed time $t$, and so, $\forall \ i \in\mcI^j$,
\begin{equation}\label{jdemand}
    \int_0^{\g_i^j(a)} f^j(z) \ dz 
    = \int_0^{\g_i^j(a)} f_i(z) \ dz,
\end{equation}
therefore $\theta_i = \theta^j, \ \forall \ i \in \mcI^j$.
Thus, any bid ouside of
our construction
has a zero valuation, with respect to buyers $\in\lambda$ and sellers
$\in\Lambda$, and therefore cannot cause shifts to occur except through a
shared buyer, e.g. some $l\in\mcI^k$. Thus, in all cases,
(\ref{buyerinversedemand}) and (\ref{sellerinversedemand}) hold. Fixing all
bids in any auction $q \ni \Lambda^j$,
we have, $\forall \ k\in\mcI_i$,
\begin{equation}\label{idemand}
    \displaystyle\int_0^{D^k} f^k(z) \ dz = \sum_{i\in\mcI^k}\int_0^{\g_i^k(a)}
f^k(z) \ dz,
\end{equation}
which holds $\forall \ k\in\mcI_i$, by (\ref{jtoi}) and Proposition
\ref{sellerstrategy}..
Finally, using (\ref{jdemand}), (\ref{idemand}), $\forall \ i\in\mcI^j, \forall \ k\in\mcI_i,\forall \ l\in\mcI^k$,
\begin{align}\label{tieqtk}
    \int_0^{\g_i^k(a)} f_i(z) \ dz &= \int_0^{\g_i^k(a)} f^k(z) \ dz,
\end{align}
and
\begin{align}\label{tkeqtl}
    \int_0^{\g_l^k(a)} f^k(z) \ dz &= \int_0^{\g_l^k(a)} f_l(z) \ dz.
\end{align}
Thus, with a slight abuse of notation for clarity,
\begin{equation}\label{funion-eq}
    \sum_{\lambda}\int_0^{\g(a)} f^\Lambda(z) \ dz =
\sum_{\Lambda}\int_0^{\g(a)} f_\lambda(z) \ dz,
\end{equation}
where the result follows by construction, and the continuity of $\theta'$.
$\qed$

@@

In order to represent the public platform of the secondary market, we model the ISP as
a kind of buyer $\kappa$ who remains at time $t=0$, i.e. does not participate
in any auctions. At time $t=0$, a seller $k$ entering the market will have
submitted bid $s_\kappa^j =(\epsilon, D^j)$ to the CMHK platform, and so the
seller does not require a priori demand information to enter the market.
Also, a new sellers' bid, $(D^j, \epsilon)$, is public knowledge. 
\iffalse
(DO I WANT UPDATES? MORE OR LESS FAIR? NEED EITHER UPDATE QUANTITY OR BOTH,
IMPLICATIONS?)
We assume that sellers update their bids with the ISP, which is modeled as a
``buyer" $\kappa$. 
\fi
A buyer entering the market
at $t=0$ is assumed to have an initial nonzero bid price, which we may assume
(SAY BETTER! ALSO DO I REALLY NEED THE I.I.D?) is initialized as 
an independently and identically distributed (i.i.d.) random variable $p_i^j=X$ with
probability $\mathcal{P}$,
$$
    \mathcal{P}[\epsilon\le X \le \kappa] =
\displaystyle\int_\epsilon^{p^\kappa} \mathfrak{f}(x) \
ds,
$$
where $p^\kappa$ is the overage charge of the ISP, and $\mathfrak{f}$ the probability
density function of $X$.
%may represent by some homogenous function of degree one (EXPAND?). 
Thus the auction
begins at time $t>0$, and at $t=0$, $j$ will increment through a single iteration,
initializing bid prices.

Consider a user seeking to prevent
data overage charges by purchasing data from a subset of other network users.
The sellers' auction will function as follows: at each bid iteration all buyers
submit bids, and the winning bid is the buyer $i$ that has the highest price
$p_i^j$. The seller allocates
data to this winner, at which point all other buyers are able to bid again, and
the winner leaves the auction (with the exception where multiple bidders bid
the same price, where (\ref{dataallocation}) determines they will not fully
satisfy their demand, and so we will assume they remain in the auction). The auction progresses as such until all the
sellers' data has been allocated. 
% SELLER ALGORITHM
\begin{center}
\begin{algorithm}[H]
\caption{(Seller progressive allocation)}
\begin{algorithmic}[1]
\State $p^{j(0)} \gets \epsilon$, $s^{j(0)} \gets (p^j, D^j)$, $\bar\mcI =
\emptyset$, compute
$\mcI^{j(0)}$
\State Update $s^j$ 
\While{$D^j(t) > 0$}
\State $\bar{i} \gets \displaystyle\max_{i\in I^j}\sum_{i\in I^j} p_i^j$ 
\State $D^{j(t+1)} \gets D^{j(t)} - \g_{\bar{i}}^{j(t)}(a)$
%\State $p^j \gets \theta_{i^*}'(d_{i^*}^j)\circ e_i$
\State $p^j \gets p_{i^*}^j+\epsilon$ and $d^j \gets D^{j(t+1)}$
\State $s^{j(t+1)} \gets (d^j, p^j)$
\State Update $s^j$
\State $\bar\mcI \gets \bar\mcI \cup \bar{i}$
\For{$k \in \bar\mcI$}
\If{$p_k^j < p_{i*}^j$}
\State $D^{j(t+1)} = d_k^{j}$
\State $\bar\mcI \gets \bar\mcI \setminus \lbrace k \rbrace$
\EndIf
\EndFor
\State Compute $\mcI^{j(t)}$
\State $\mcI^{j(t+1)} = \mcI^{j(t)}\setminus \bar\mcI$
\State $t \gets t+1$
\EndWhile
\end{algorithmic}
\end{algorithm}
\end{center}
Each time step, $s^j$ is updated it is shared with all
participating buyers. At this point buyers have the opportunity to bid again,
where a buyer that does not bid again is assumed to hold the same bid, since a
buyer dropping out of the auction will set their bid to $s_i^j=(0,0)$.

@@

The property of truthfullness is an essential component of equilibrium in
second-price markets. The strategies described in this paper have removed the
necessity for a user to determine its own valuation function, we intend to show that the market dynamics resulting from the
construction of the user strategy space results in truthful bids that are optimal for all users,
i.e. bid prices are to the marginal value as determined by market dynamics. 
To achieve incentive compatibility, we find that the opt-out buyer must choose
this subset so that its overall marginal value is greater than its market price.
We have so far only made the \emph{assumption} of truthful bids throughout our analysis. As was shown in Lemma \ref{userunion}, a buyer only
has incentive to change its bid as a result of a market shift or partial
allocation. We now show the necessary condition of a truthful reply, new bid
prices must differ from the last by at least $\epsilon$, and prove that the
resulting bid is an $\epsilon$-best response, supporting our strategic analysis.
In a truthful reply, the term $\epsilon/\theta_i'(0)$
ensures that a new bid price differs from the last bid price by at least
$\epsilon$, thereby ensuring that a buyer does not change its bid without
correcting the effects of unstable shifts.
We argue that if truthfulness holds \emph{locally} for both buyers and sellers, i.e. $p_i ={\theta_i}' \
\forall \ j \in \mcI_i$ and $p^j = {\theta^j}' \ \forall \ i \in\mcI^j$, then
there exists a local market equilibrium extending over a subset of connected
local markets. We have the following Proposition. 
(DO I NEED TO PROVE CONTINUITY TOO?)

@@

\proposition{(Incentive compatibility across local auctions)}\label{incentive}

@@

\corollary{(Seller cooperation)}

@@

The data-sharing market consists of a inter-dependent sets of these
multi-auction games around fixed points.  Clearly, the union of all possible
sets $\bigcup_{j\in\mcI} \Delta^j$ covers $\mcI$. We claim that the shared buyers
between the different subsets $\Delta$ form a heirarchical structure, and that
there can only be a single primary fixed point, and this seller determines
the equilibrium price in the global market. (EXPAND) We have the following
Corollary, 
{
\corollary{(Primary fixed point)}
Let the set of shared buyers be denoted as,
$\underline{\lambda} = \bigcap_{j\in\mcI} \lambda^j$, and the set of all
sellers as, $\overline{\Lambda} = \bigcup_{j\in\mcI}\Lambda^j$. If
$\overline{\Lambda}$ is not a partition, i.e. $\nexists \ j,k
\in\overline{\Lambda}$ such that $\Lambda^j \cap \Lambda^k = \emptyset$, then
$\exists \ j \in\overline{\Lambda}$ such that $p_*^j \ge p_*^k, \ \forall \
k\ne j\in\overline{\Lambda}$. 
}\\
\textbf{Proof:}
We assume a finite number of users, with continuous valuation functions bounded both
above and below. From the assumption that $\overline{\Lambda}$ is not a
partition, we have that,
$$
    \limsup\limits_{j\to I} \overline{\Lambda} =  \bigcap_{j\ge 1}\bigcup_{k\ge j} \Lambda^k,
$$
is the primary seller $j$, and we have the market price $p_*^j$ from,
$$
    \liminf\limits_{i\to I} \overline{\lambda} = \bigcup_{i\ge 1}\bigcap{k\ge i}
\lambda^k,
$$
and the result follows from Lemma \ref{uservaluation}, Proposition
\ref{userunion} and Proposition \ref{incentive}.
$\qed$\\
(USE BOREL-CANTELLI WITH I.I.D? FUTURE WORK?)
